---
title: "Assignment B-1"
author: "Jingwen Zhou"
output: github_document
---

### Load libraries
```{r}
suppressMessages(library(datateachr))
suppressMessages(library(datateachr))
suppressMessages(library(testthat))
suppressMessages(library(tidyverse))
suppressMessages(library(dplyr))
suppressMessages(library(scales))
suppressMessages(library(gapminder))
suppressMessages(library(palmerpenguins))
```

### Exercise 1 & 2: Make a Function & Document the Function
```{r}
#' Summary statistics or numeric variable
#' 
#' @description
#' This function do the summary statistics of one given numerical variable 
#' across the groups of another given variable in a given dataset. 
#' It also calculates density estimates between two variables and 
#' plots the data using the ridgeline visualization. 
#'
#' @param data The dataset which need to be explore. 
#' This parameter is named `data` because it tells the user intuitively that 
#' we need a dataset as the first parameter.
#' 
#' @param x The numeric column name, which need to be summarized
#' This parameter is named `x` because when I plot the ridgeline graph to show the 
#' distribution, the x-axis is corresponding to this numeric variable.
#' 
#' @param y Another column name, the dataset can be grouped by this variable
#' This parameter is named `y` because when I plot the ridgeline graph to show the 
#' distribution, the y-axis is corresponding to this variable.
#' 
#' @return summarise_result: A list which contains the mean, range, median of numeric variable
#' 
#' @examples
#' result1 <- fun(apt_building, year_built, storey_height)
#' result2 <- fun(penguins, body_mass_g, species)
#' result3 <- fun(gapminder, lifeExp, continent)
#' 
fun <- function(data, x, y) {
  calculations <- summarise(data,
                            is_numeric_x = is.numeric({{x}}),
                            class_x = class({{x}}))
  
  if (!calculations$is_numeric_x){
    stop("Selected column is not numeric. ",
         "Class of x is: ",
         calculations$class_x)
  }
  summarise_result <- data %>%
    group_by({{y}}) %>%
    summarise(mean = mean({{x}}, na.rm = TRUE),
              range = range({{x}}, na.rm = TRUE),
              median = median({{x}}, na.rm = TRUE),
              .groups = 'keep')
  
  plot <- data %>%
  ggplot(aes({{x}}, {{y}})) +
  ggridges::geom_density_ridges(alpha = 0.5)
  print(plot)
  
  return(summarise_result)
  
}

```
 
### Exercise 3: Include examples
Example 1 uses apt_buildings dataset to test the function. The first argument passed to the function is apt_building, which is a tibble (list). The second argument and the third argument are the column name which I want to explore. I want to get the summarise ouput which include the range, mean and median of variable 'year built' across the groups of storey height from the data.
```{r}
# Example 1: Use `apt_buildings` dataset
apt_building <- apt_buildings %>%
  mutate(storey_height = case_when(no_of_storeys < 5 ~ "very low",
                                 no_of_storeys < 10 ~ "low",
                                 no_of_storeys < 20 ~ "moderate",
                                 no_of_storeys < 30 ~ "high",
                                 TRUE ~ "very high"))

result1 <- fun(apt_building, year_built, storey_height)
result1
```

Example 2 uses penguins dataset to test the function. Use different dataset is to make sure that the function is not limited to specific inputs, and don't have the magic numbers.

```{r}
# Example 2: Use `penguins` dataset
result2 <- fun(penguins, body_mass_g, species)
result2
```

Exaple 3 shows how an error can be thrown in the function, if the second argument is not a numeric column name, the function will stop running and throws an error "Selected column is not numeric. Class of x is: factor (or other type that is not numeric)". This is because in our function we need to calculate the mean, median and range on of this parameter, it must be of type numeric.
```{r error=TRUE}
# Example 3: Use `gapminder` dataset
result3 <- fun(gapminder, country, continent)
```

### Exercise 4: Test the Function
```{r}
# expect_type(x, type) checks that typeof(x) is type.
# In this function, we check if the output type is consistent (all output is `list` type) 
test_that("The function returns a list", {
  expect_type(result1, "list")
  expect_type(result2, "list")
})
```
```{r}
# expect_error() check that code throws an error with a message
# The second parameter should be numeric column name, this will cause function throw an error
test_that("Test the function input type", {
  expect_error(fun(gapminder, country, continent))
})
```
```{r}
# Use expect_equal() to check the output content
sum <- penguins %>% # manually summarise the data
  group_by(species) %>%
  summarise(mean = mean(body_mass_g, na.rm = TRUE),
            range = range(body_mass_g, na.rm = TRUE),
            median = median(body_mass_g, na.rm = TRUE),
            .groups = 'keep')

test_that("Test the output content", {
  expect_equal(result2, sum) # result2 is the return output of the function
})
```



